Implementing DNS in C0

### 2017-12-08 paper.tex

\begin{abstract}
  Please write an abstract.
\end{abstract}

@@

\subsection{What is DNS?}

Farzaneh

@@

\subsection{75\%}

@@

\subsection{100\%}

@@

\subsection{125\%}

@@

For performance analysis, we plan to evaluate our nameserver for latency and throughput, as these appear to be the most important metrics for \Kwd{DNS} performance. We plan to do this using one of two pieces of software\cite{github:dnsperf1, github:dnsperf2} (confusingly, both named \texttt{dnsperf}), which read queries from a file and then send these requests to a nameserver. The tools mentioned in \cite{github:dnsperf2} seem better-suited to our needs, as those of \cite{github:dnsperf1} appear to not give latency information in a useful fashion. We will compare our results (at various load levels) to existing \Kwd{DNS} software (though we have yet to determine which specific software to take as our baseline). One remaining difficulty in evaluation lies in figuring out what sort of query workload to use --- the performance analysis tools we have looked at suggest using an input file with somewhere on the order of one million queries, which is more than can feasibly be generated by hand. However, there does not appear to be a standard benchmark for this testing as there are for many other systems. We will likely generate large test files in a randomized way, but do not have a good sense of how to make these files accurately reflect realistic usage.

\nocite{rfc:1034, rfc:1035}
\bibliographystyle{abbrv}
\bibliography{bibtex-references/refs,project}

>>>>

\begin{abstract}
  We are implementing a \Kwd{DNS} server in the \Kwd{C0} language,
  which we intend to evaluate for both safety and performance.
\end{abstract}

@@

\Kwd{Domain Name System} (\Kwd{DNS}) is a hierarchical database that
maps domain names to IP addresses in a distributed manner augmented
with caching to achieve a better
performance~\cite{rfc:1034,rfc:1035,mun-lee:2005}. In fact, there are
three major parts:

\begin{enumerate}
\item Domain name space with resource records: The domain name space
  is a tree-like data structure with a root, and nodes labeled with at
  most 63 characters. The domain name of a label is the sequence of
  labels on the path from the node to the root. Each node of the tree,
  associated with a domain name, has a set of resource records.

\item Name servers keep information about a complete sub-tree of the
  domain name. They may also cache pointers to other name
  servers.

\item Resolvers are responsible for sending a query to name servers
  upon clients request and extract information from them. They may
  also have some parts of the name space cached themselves.  In fact,
  their role is to provide an interface between applications and DNS
  in the process of \emph{name resolution}. Name resolution starts
  when an application program (the host) sends its query for an IP
  address to a local name server, continues by the local name server
  which extracts the information in an iterative/recursive manner from
  different name servers (If it does not already have it in its own
  cache), and ends when the local name server returns the IP address
  to the host.
\end{enumerate}

The messages exchanged between host and name servers adhere to a
simple format, which is divided into 5 sections: (1) Header, (2)
Question, (3) Answer, (4) Authority, and (5) Additional.  Each of
these sections also has its own special format, some of which will be
covered in more detail in next parts of this document.

@@

\subsection*{75\%}

@@

\subsection*{100\%}

@@

\subsection*{125\%}

@@

For performance analysis, we plan to evaluate our nameserver for
latency and throughput, as these appear to be the most important
metrics for \Kwd{DNS} performance. We plan to do this using one of two
pieces of software\cite{github:dnsperf1, github:dnsperf2}
(confusingly, both named \texttt{dnsperf}), which read queries from a
file and then send these requests to a nameserver. The tools mentioned
in~\cite{github:dnsperf2} seem better-suited to our needs, as those
of~\cite{github:dnsperf1} appear to not give latency information in a
useful fashion.

We will compare our results (at various load levels) to existing
\Kwd{DNS} software (though we have yet to determine which specific
software to take as our baseline). One remaining difficulty in
evaluation lies in figuring out what sort of query workload to use ---
the performance analysis tools we have looked at suggest using an
input file with somewhere on the order of one million queries, which
is more than can feasibly be generated by hand. However, there does
not appear to be a standard benchmark for this testing as there are
for many other systems. We will likely generate large test files in a
randomized way, but do not have a good sense of how to make these
files accurately reflect realistic usage.

\bibliographystyle{abbrv}
\bibliography{bibtex-references/refs,project}
